\chapter{Gauge Fields and Instantons}

Connections as $1$-forms.

Gauge potentials.

Distribution of horizontal spaces.

Manufacture large supply of connection forms on the Hopf bundle $S^7\to S^4$. Put in simply standard form thanks to Iwasawa Decomposition of $SL(2, \bb H)$

Physicist's Gauge equivalence -> Moduli Space of connections

Connection -> path lifting, parallel translation

Curvature as covariant derivative. Cartan Structure equation.

Local field strenths. Transformation properties.

\rtext{Informal: physical origin of instantons and of notion of (anti-) self duality}.

Hodge star.

Anti-self-dual connection on the Hopf bundle $S^7 \to S^4$ : Moduli space of anti-self-dual connections on the Hopf bundle.

Anti-self-dual moduli space identified with $(0, \infty)\times \RR^4$ and then parametrized as $B^5$ with compactification $D^5$. THis has as boundary $S^4$: set of ``concentrated'' connections

Gauge field ~ newtonian force

Matter fields

Dynamical equation that ``couples'' matter fields to gauge fields; physicists formulate it in terms of covariant derivative.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Connections and Gauge Equivalence}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Curvature}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Yang-Mills FUnctional}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Hodge Dual for $2$-Forms in Dimension $4$}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Moduli Space}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Matter Fields: Motivation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Associated Fiber Bundles}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Matter Fields and their Covariant Derivatives}